---
title: "Weight of Fish"
author: "Kimberly Orantes"
date: "Year 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(leaps)
mydata <- read.csv(file ="Fish.csv")
perch <- filter(mydata, Species == "Perch")
perch <- select(perch, -Species)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


```{r}
perchMODL <- lm(Weight~ Height+Width,data=perch)
summary.lm(perchMODL)
```

The best two regression model to predict the weight of perch is Height and Width variables. This regression model is the best overall as well with an adjusted R-squared of 0.94.  

# Pike

```{r}
Pike <- filter(mydata, Species == "Pike")
Pike <- select(Pike, -Species)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

```{r}
PikeMODL <- lm(Weight~ Length1+Length3,data=Pike)
summary.lm(PikeMODL)
```

The best two regression model to predict weight of Pike is Length1 and Length3 variables with an adjusted R-squared of 0.9649. This is two regression model is not the best overall, the best overall would be the regression model with all the variables.   
  
# Roach

```{r}
Roach <- filter(mydata, Species == "Roach")
Roach <- select(Roach, -Species)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

```{r}
RoachMODL <- lm(Weight~ Length3+Width,data=Roach)
summary.lm(RoachMODL)
```

The best two regression model to predict weight of Roach is Length3 and Width variables. This the best regression model overall with an adjusted R-squared of 0.8482.  
  

# Plots

```{r}
basicNN <- ggplot(perch,aes(y=Weight,x=Height))
basicNN + geom_point() + geom_smooth(method=lm) + ggtitle("Perch")
```

```{r}
basicNN <- ggplot(perch,aes(y=Weight,x=Width))
basicNN + geom_point() + geom_smooth(method=lm) + ggtitle("Perch")
```

These two Perch plots show the distribution of the best two regression model variables to predict weight, Height and Width. In both plots we can see that when the variables Height and Width increase the Weight increases as well. This demonstrates there is a relationship between weight and each of the variables Height and Width.    
   
# Discussion and Conclusion
<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


  