---
title: "Weight of Fish"
author: "Kimberly Orantes"
date: "Year 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(leaps)
mydata <- read.csv(file ="Fish.csv")
perch <- filter(mydata, Species == "Perch")
perch <- select(perch, -Species)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


```{r}
perchMODL <- lm(Weight~ Height+Width,data=perch)
summary.lm(perchMODL)
```

The best two regression model to predict the weight of perch is Height and Width variables. This regression model is the best overall as well with an adjusted R-squared of 0.94.  

# Pike

```{r}
Pike <- filter(mydata, Species == "Pike")
Pike <- select(Pike, -Species)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

```{r}
PikeMODL <- lm(Weight~ Length1+Length3,data=Pike)
summary.lm(PikeMODL)
```

The best two regression model to predict weight of Pike is Length1 and Length3 variables with an adjusted R-squared of 0.9649. This is two regression model is not the best overall, the best overall would be the regression model with all the variables.   
  
# Roach



